Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
typo
fix little

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_\beta(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_{\beta}(\dataobs)})}
\end{equation*}
The previous mechanism is very similar to the exponential mechanism as defined in \cite{expmech},  with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$, which is :
\[
   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),-)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
 \]

 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\dataobs'$ (w.r.t $\ell_1$ norm)
 of the function
 \[\hellinger \circ \langle (\bysinfer(\dataobs', \cdot), \bysinfer(\cdot, \cdot)\rangle\]
 that is:
 \begin{equation*}
 \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}
Notice that we maximize also over $r$\todo{need to explain why}.
\subsection{Analysis of the mechanism}
In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

>>>>

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_\beta(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_{\beta}(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$, which is :
\[
   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
 \]

 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\dataobs'$ (w.r.t $\ell_1$ norm)
 of the function
 \[
 \hellinger \circ \langle (\bysinfer(\dataobs'), \cdot), (\bysinfer(\cdot),\cdot)\rangle,
 \]
 that is:
 \begin{equation*}
 \max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

\subsection{Analysis of the mechanism}
In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.
